Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-01-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of geological formations that may affect the oil production. Important factors during flooding operations are the volumetric sweep efficiency, or the ration of volumes between the recovered and the injected fluids as well as the breakthrough of injected fluid. A major problem associated with water-flooding projects is the early water-breakthrough, the main causes of which are high-permeability layers and unfavorable mobility ratios. Water breakthrough is the main determinant of the productive life of the reservoir \citep{riaz_2004, tavassoli_2015}. During immiscible CO$_{2}$ flooding $\left(\text{\eg in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, density of supercritical CO$_{2}$ is usually lower than hydrocarbons, thus viscous fingering and/or channelling may occur.

>>>>

\begin{enumerate}
  \item \green{Try do avoid (as much as possible) the use of \underline{{\bf 'we'}} in technical/academic writing;}
  \item \green{\underline{\bf Motivation} means:
    \begin{itemize}
      \item Why is the subject of study important?
      \item What sort of applications will this study impact upon?
    \end{itemize}}
  \item \green{\underline{\bf Main aim} means:
    \begin{itemize}
      \item What is the main goal of this study?
    \end{itemize}}

\end{enumerate} 
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, permeability and/or porosity characteristics in different zones) of geological formations. A major problem associated with water-flooding processes is the early water-breakthrough caused by high-permeability layers and unfavorable mobility ratios. Water breakthrough and volumetric sweep efficiency (ratio of volumes between the recovered and the injected fluids) are the main determinants of the productive life of the reservoir \citep{riaz_2004, tavassoli_2015}. During immiscible CO$_{2}$-flooding $\left(\text{\eg in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, density of supercritical CO$_{2}$ is usually lower than hydrocarbons, thus viscous fingering and/or channelling may occur.
